---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# kwm

kwm provides very simiple wrapper functions to produce **K**ey**W**ord **M**odels that produce classification predictions based on explicit lists of regular expression pattern matches. 
By supplying a generic prediction function for such lists, it is easy to compare the performance of very simple regex matching to other, more complicated text classification models within the same pipeline.

## Installation

You can install kwm from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mdlincoln/kwm")
```

## Example

```{r example}
library(kwm)

month_df <- data.frame(month = month.name, stringsAsFactors = FALSE)

# Locate all matches that INCLUDE either "a" or "e" but EXCLUDE any ending in "r"
month_model <- kwm(include = c("a", "e"), exclude = "r$", varname = "month")

predict(month_model, newdata = month_df)
```
